---
title: "Example of the Cental Limit Theorem for Uniform Distribution"
author: "Craig W. Slinkman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is an example of how the sampling distribution of an continuous niform Distribution approaches the normal distribution as the size of the random sample increases.  We will use simulation in this study.

## Definition of a continuous uniform distribution  

[Wikipedia]([linked phrase](http://example.com) defines a continuous distribution as:

>In probability theory and statistics, the continuous uniform distribution or rectangular distribution is a family of symmetric probability distributions. The distribution describes an experiment where there is an arbitrary outcome that lies between certain bounds.[1] The bounds are defined by the parameters, a and b, which are the minimum and maximum values. The interval can either be closed (e.g. [a, b]) or open (e.g. (a, b)).[2] Therefore, the distribution is often abbreviated U (a, b), where U stands for uniform distribution.[1] The difference between the bounds defines the interval length; all intervals of the same length on the distribution's support are equally probable. It is the maximum entropy probability distribution for a random variable X under no constraint other than that it is contained in the distribution's support.[3]

The probability density function for a continuous uniform distribution is:

$f(x) =
\left\{ 
  \begin{array}{ c l }
    \frac{1}{b-a} & \quad \textrm{if } a \leq x \leq b  \\
    0                 & \quad \textrm{otherwise}
  \end{array}
\right.$

A plot of the xontinuous distribution density function whenb $a = 10$ and $b = 90$ is show in Figure 1.

```{r}
 require(tidyverse)                   # I live in the tidy verse.
 require(cowplot)                     # For publishable graphics
 require( here )                      # To get project location in file system.


source("D:/R-Projects/RStatistics/plot_distribution.R")

 
 a <- 10                                     # Assign parameter values.
 b <- 90
 
 x <- seq( from = 0,                         # Define random variable values.
           to   = 100,
           by   = 0.5 )
 
 density <-                                  # Compute probability density function
   ifelse( x < a, 0,
           ifelse( x <= b, 1/(b-a), 0 ))
 
 this_tibble <-                              # Create tibble for plotting.
   tibble( x, density )
 
 figure_01 <-
   ggplot( this_tibble,                        # plot graph
           aes( x = x, 
                y = density )) +
   geom_line() +
   xlab( "X" ) +
   ylab( "Probability density" ) +
   ggtitle( "Figure 1: Probability of continuous uniform fensity with\n",
            "paraameters a = 10, b = 90 " ) +
   theme_cowplot()
 
figure_01

 
 plots <-                                 # Build plot directory path.
   file.path( here(),
              "plots" )
 
 figure_01                                # Display plot.
 
 ggsave( "figure_01.png",                 # Save plot for quora answer.
         plot = figure_01,
         path = plots )
```
 The mean of thie continuous uniforms distrinution is given by 
   
  $$\mu = \frac{a + b}{2}$$
  and the standard deviation if given by 
  
$$\sigma = \sqrt{ \frac{1}{12}}( b - a )$$

So in our case the mean of our distribution with $a = 10$ and $b = 90$ is
$$\mu = \frac{10 + 90}{2} = 50$$

and the standard deviation is 

$$\sigma = \sqrt{\frac{1}{12}}( 90 - 10 ) = 23.09401 \approx 23.09$$

## Drawing a random sample

We will now see the effect of various sample sizes on the sahape of the sampleing distribution.  
We will draw 1000 random sample of various sizes.  We will start with a sample size of and double them sample size until we reach a sample size of 128.

### Sample size of n = 1

```{r}
# In this code we com[pute the sampling distribution for the samples sizes we
# listed anove.

set.seed( 11235 )                           # For reproduciability of results.

a = 10
b = 90
n <- c( 1, 2, 4, 8, 16, 32, 64, 128 )

means <- rep( NA, 8000 )
means <- matrix( means, nrow = 1000 )

 
for( j in 1:length(n) ){
  for( i in 1:1000 ){
    our_sample <- runif( n[j], min = a, max = b )
    means[i,j] <- mean( our_sample )
  }
}
  

```

The sampling distribution for the sample sizes of 1 is shown below:



```{r}
source("D:/R-Projects/RStatistics/plot_distribution.R")

sampling_distribution <-
  means[,1]

figure_03 <-
  plot_distribution( sampling_distribution,
                    expression(bar(X)),
                    "Figure 2: Sampling distribution with n = 1" )
figure_03

 require(tidyverse)                   # I live in the tidy verse.
 require(cowplot)                     # For publishable graphics
 require( here )                      # To get project location in file system.
 
 a <- 10                                     # Assign parameter values.
 b <- 90
 
 x <- seq( from = 0,                         # Define random variable values.
           to   = 100,
           by   = 0.5 )
 
 density <-                                  # Compute probability density function
   ifelse( x < a, 0,
           ifelse( x <= b, 1/(b-a), 0 ))
 
 this_tibble <-                              # Create tibble for plotting.
   tibble( x, density )
 
 figure_01 <-
   ggplot( this_tibble,                        # plot graph
           aes( x = x, 
                y = density )) +
   geom_line() +
   xlab( "X" ) +
   ylab( "Probability density" ) +
   ggtitle( "Figure 2: Sampling distribution with n = 3.")
   theme_cowplot()
 
figure_03                                 # Display plot.
 
 ggsave( "figure_03.png",                 # Save plot.            
         plot = figure_03,
         path = plots )
  
```
This plot shows the empirical histogram with a density smooth.  If we sample frpm a population an infinite number of times the sampling distribution of size one will be equal to the population being sampled.  However because our samples are only of size 1,000 from the population the histogram shows a differing numbering of observation per bin.  

The line on the histogram is called a density smoother.  In statistics to [smooth a data set](https://en.wikipedia.org/wiki/Smoothing) is to create an approximating function that attempts to capture important patterns in the data, while leaving out noise or other fine-scale structures/rapid phenomena. It is a way of dealing with the inherit randomness of noise in our data.


### Sample size of 3.

The sampling distribution of the mean for sample size of 2 is shown in Figure 3.

```{r}
set.seed( 11235 )                    #  For reproducability of results.

a = 10                               # Set uniform parameters
b = 90

n <- c( 1,                           # Set sample sizes
        2,
        4,
        8,
        16,
        32,
        64,
        128 )

means <-                            # Create matrix to hold means 
  rep( NA, 8000 )
means <-                            # Columns represent different sample sizes
  matrix( means,                    # and rows represent different samples.
          nrow = 1000 )


for( j in 1:length(n) ){            # Loop through sample sizes
              
  for( i in 1:1000 ){               # Loop through samples.
    
    our_sample <-                   # Sample uniform distribution
      runif( n[j], 
             min = a, 
             max = b )              
    
    means[i,j] <-                   # Compute sample means.
      mean( our_sample )
  }
}

sampling_distribution <-
  means[,2]

figure_03 <-
  plot_distribution( 
    sampling_distribution,
    expression(bar(X)),
    "Figure 3: Sampling distribution with n = 2" )
    
figure_03                                   # Display plot.
                              

ggsave( "figure_03.png",                    # Save plot.            
        plot = figure_03,
        path = plots )
```

