---
title: "Example of the Cental Limit Theorem for Uniform Distribution"
author: "Craig W. Slinkman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is an example of how the sampling distribution of an continuous niform Distribution approaches the normal distribution as the size of the random sample increases.  We will use simulation in this study.

## Definition of a continuous uniform distribution  

[Wikipedia]([linked phrase](http://example.com) defines a continuous distribution as:

>In probability theory and statistics, the continuous uniform distribution or rectangular distribution is a family of symmetric probability distributions. The distribution describes an experiment where there is an arbitrary outcome that lies between certain bounds.[1] The bounds are defined by the parameters, a and b, which are the minimum and maximum values. The interval can either be closed (e.g. [a, b]) or open (e.g. (a, b)).[2] Therefore, the distribution is often abbreviated U (a, b), where U stands for uniform distribution.[1] The difference between the bounds defines the interval length; all intervals of the same length on the distribution's support are equally probable. It is the maximum entropy probability distribution for a random variable X under no constraint other than that it is contained in the distribution's support.[3]

The probability density function for a continuous uniform distribution is:

$f(x) =
\left\{ 
  \begin{array}{ c l }
    \frac{1}{b-a} & \quad \textrm{if } a \leq x \leq b  \\
    0                 & \quad \textrm{otherwise}
  \end{array}
\right.$

A plot of the xontinuous distribution density function whenb $a = 10$ and $b = 90$ is show in Figure 1.

```{r}
require(tidyverse)                          # I live in the tidy verse.
require(cowplot)                            # For publishable graphics

a <- 10                                     # Assign parameter values.
b <- 90

x <- seq( from = 0,                         # Define random variable values.
          to   = 100,
          by   = 0.5 )

density <-                                  # Compute probability density function
  ifelse( x < a, 0,
  ifelse( x <= b, 1/(b-a), 0 ))

this_tibble <-                              # Create tibble for plotting
  tibble( x, uniform )

figure <-
  ggplot( this_tibble,                        # plot graph
          aes( x = x, 
               y = density )) +
    geom_line() +
    xlab( "X" ) +
  ylab( "Probability density" ) +
  ggtitle( "Figure 1: Probability of continuous uniform fensity with\n",
           "paraameters a = 10, b = 90 " ) +
  theme_cowplot()

require( here )                          # Determine project location in file
                                         # system.

plots <-                                 # Build plot directory path.
  file.path( here(),
             "plots" )

figure_01                                # Display plot.

# ggsave( "figure_01.png",
#         plot = figure_01,
#         path = plots )
```
 The mean of thie continuous uniforms distrinution is given by 
   
  $$\mu = \frac{a + b}{2}$$
  and the standard deviation if given by 
  
$$\sigma = \sqrt{ \frac{1}{12}}( b - a )$$

So in our case the mean of our distribution with $a = 10$ and $b = 90$ is
$$\mu = \frac{10 + 90}{2} = 50$$

and the standard deviation is 

$$\sigma = \sqrt{\frac{1}{12}}( 90 - 10 ) = 23.09401 \approx 23.09$$

## Drawing a random sample

We will now see the effect of various sample sizes on the sahape of the sampleing distribution.  
We will draw 1000 random sample of various sizes.  We will start with a sample size of and double them sample size until we reach a sample size of 128.

### Sample size of n = 1

```{r}
# In this code we com[pute the sampling distribution for the samples sizes we
# listed anove.

set.seed( 11235 )                           # For reproduciability of results.

a = 10
b = 90
n <- c( 1, 2, 4, 8, 16, 32, 64, 128 )

means <- rep( NA, 8000 )
means <- matrix( means, nrow = 1000 )

 
for( j in 1:length(n) ){
  for( i in 1:1000 ){
    our_sample <- runif( n[j], min = a, max = b )
    means[i,j] <- mean( our_sample )
  }
}
  

```

The sampling distribution for the sample sizes of 1 is shown below:



```{r}
source("D:/R-Projects/RStatistics/plot_distribution.R")

sampling_distribution <-
  means[,1]

Figure_02 <-
  plot_distribution( sampling_distribution,
                    expression(bar(X)),
                    "Sampling distribution with n = 1" )
Figiur_02
  
```
This plot shows the empirical histogram with a smooth.  Theoretically this histogram should lool like the 
